%-------------------------
% Resume in Latex
% Author : Nikan Doosti
%------------------------

\documentclass[letterpaper,11pt]{article}

% \include{command.tex}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\LinedItem}[1]{\item \begin{tabular}[t]{|p{10cm}}#1\end{tabular}}

\newcommand{\resumeSubheading}[5]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ 
      \textit{\small#3} & \textit{\small #4} \\
      \textit{#5} & 
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingF}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ 
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\awarditem}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\ 
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\awarditemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\awarditemListEnd}{\end{itemize}\vspace{-5pt}}
    


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nikan Doosti}} % (Legal Name: Mohammad DoostiLakhani) 
  &
  Email: \href{mailto:nikan.doosti@outlook.com}{nikan.doosti@outlook.com}\\
   & Web: \href{https://www.nikronic.com/}{https://www.nikronic.com}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
 \resumeSubHeadingListStart
   \resumeSubheadingF
     {Iran University of Science and Technology (IUST)}{Tehran, Iran}
     {Master of Science in Computer Engineering - Artificial Intelligence}{Aug 2019 - Dec 2022}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis:} High Resolution Neural Topology Optimization via Differentiable Physics Engine}
        \resumeItem{\textbf{Defense:} Achieved \textbf{maximum score} during defense on \textit{Oct 22, 2022} with \textbf{GPA of 17.17/20.00}}
        \resumeItem{\textbf{IUST:} This university is one of the most prestigious in the country, being in \textbf{top-4} consistently.}
      \resumeItemListEnd
   \resumeSubheadingF
     {University of Guilan (UoG)}{Rasht, Iran}
     {Bachelor of Science in Computer Engineering}{Aug 2015 - Aug 2019}
     \resumeItemListStart
        \resumeItem{\textbf{Final Project:} Descreening and Rescreening of Halftone Images via Data-Driven Deep Learning Methods}
        \resumeItem{\textbf{Class Rank:} Graduated \textbf{3rd} out of 55 with a \textbf{GPA of 18.64/20.00}}
      \resumeItemListEnd
 \resumeSubHeadingListEnd
%-------------------------------------------

%--------Publications------------------
\section{Publications}
\label{sec:publication}
 \resumeSubHeadingListStart
   \resumeItem{\textbf{Doosti, Nikan}, Julian Panetta, and Vahid Babaei. "Topology Optimization via Frequency Tuning of Neural Design Representations." In \textbf{Symposium on Computational Fabrication}, pp. 1-9. 2021. (\href{https://dl.acm.org/doi/abs/10.1145/3485114.3485124}{ACM})}
\resumeSubHeadingListEnd
%-------------------------------------------

%--------TALKS------------------
\section{Talks}
 \resumeSubHeadingListStart
   \resumeItem{"Neural Design Representations." \textbf{Toronto Geometry Colloquium Advised by Alec Jacobson} - University of Toronto. March 4, 2022. toronto-geometry-colloquium.github.io. (Length: 10 mins., \href{https://youtu.be/FdPwG2kNv0M}{Video})} 
\resumeSubHeadingListEnd
%-------------------------------------------

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant (remote)}{Saarbr{\"u}cken, Germany}
      {\href{http://aidam.mpi-inf.mpg.de/?view=home}{Artificial Intelligence aided Design and Manufacturing Group} 
      }{Jul 2020 - Mar 2021}{Max Planck Institute for Informatics}
     
      \resumeItemListStart
        \resumeItem{\textbf{Project Overview:} Novel self-supevised neural method for obtaining the optimum design showcased in Topology Optimization}
        \resumeItem{\textbf{Collaboration}: Supervised by \href{http://aidam.mpi-inf.mpg.de/?view=people_vahid} {\textbf{Dr. Vahid Babaei}} and collaborated with \href{https://www.julianpanetta.com/}{\textbf{Prof. Julian Panetta}} from the University of California, Davis, USA.}
        \resumeItem{\textbf{Interdisciplinary Learning}: Successfully navigated and mastered new topics outside my primary field, such as mechanical engineering, through self-directed learning.}
        \resumeItem{\textbf{Experiment Management}: Managed large-scale experiments by developing customized logging solutions and using MLflow to track and report results, particularly enabling easy follow-up near deadline.}
        \resumeItem{\textbf{Team Collaboration}: Actively supported group members by sharing expertise in AI, particularly in implementing mathematical models with PyTorch, and optimized workflows by guiding the team in using Slurm clusters effectively.}
        \resumeItem{\textbf{Commitment:} Dedicated over 1500 hours to research and development, demonstrating a strong commitment to the project and its outcomes.}
        \resumeItem{\textbf{Outcome:} Resulted in a master's thesis and a paper that was published and presented at the ACM Symposium on Computational Fabrication 2021 (see \hyperref[sec:publication]{Publications})}
        
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
%-------------------------------------------
  
%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full-time Data Engineering and Data Science Specialist}{Karaj, Iran}
       {Specializing in Data-driven Decision Making for Business Optimization}
      {Apr 2022 - Dec 2023}{\href{https://nahalgasht.com/}{Nahal Gasht}}
     
      % {Here is the description:
      % 1. The problem: Tourism unlike its fun nature, has its own issues, particularly acquiring Visa. Now, we have tone of people interested in international tourism but not all can have satisfying application for a successful visa. Given huge number of calls (ignoring online platforms entirely) which is about 1000 calls per day, there was a huge overhead for the personnel to figure out whom they should prioritize as many of those calls had no or little chance of getting a visa. Also, we had limited personnel, and it was not possible to handle serious potential customers with high focus and low error in administration process without sacrificing more calls. This issue, resulted in huge costs, as a slightest error would have been fatal for the customer.
      % 2. What I did: As an artificial intelligence specialist, I figured out, instead of overwhelming the expert personnel with low likelihood customers (which only could be figured out after many minutes of consulting, we can automate the entire screening process; from communication with the customer (a), over customer data acquisition (b), to prioritizing the application of the customer (c). 
      % For step (a), a speech2text system would filter calls that have basic questions or had very weak application. Given that we had no labeled clean data, I decided that we better buy such service from third-party companies. Given the importance of privacy, I integrated an offline solution. Step (b) was more challenging as there were no solution at all available, hence I had to prepare our own data. Hence, I designed and implemented a full pipeline of automated data extraction, transformation, and preprocessing dealing with low/unlabeled data regime that reduced bad data by \%35. In the final step (c), a machine learning system (XGBoost) in combination with ExplainableAI was used to not only prioritize customers, but also explain the reason for each factor affecting the likelihood of each customer as it was necessary to communicate reasoning for such decision. 
      % 3. The results: Through the success of this project, I managed to reduce the total error of personnel by \%10, preventing the company from losing around 5.5 times of my salary. Also, I have been awarded with "Most Zealous" and "The Jedi" for working hard and being an inspiring leader respectively, resulting in two promotions and \%70 (normalized by inflation - raw \%125) increase in salary within a year.}

      \resumeItemListStart
        \resumeItem{The Problem: \textbf{Implemented an AI-driven solution to address the challenge of prioritizing customers applications in the tourism sector.}}
        \resumeItem{Impact: Decreased personnel error by 10\%, \textbf{mitigating potential losses equivalent to 5.5 times my annual salary.} Also, \textbf{awarded for dedication and leadership}, leading to two promotions and a 70\% salary increase within one year. Moreover, \textbf{I established myself as the primary resource for onboarding and training} new team members, receiving praise for my ability to simplify fundamental concepts.}
        \resumeItem{Developed a comprehensive screening process automation from customer communication to application prioritization, filtering calls based on the complexity of inquiries, \textbf{reducing manual workload by 40\%.}}
        \resumeItem{Oversaw the development of a proprietary data extraction and preprocessing pipeline, resulting in a \textbf{35\% reduction in poor-quality data}.}
        \resumeItem{Deployed classical machine learning models alongside deep learning methods, coupled with Explainable AI techniques to prioritize applications and provide transparent reasoning for each decision.}
        \resumeItem{This experience demonstrates my ability to leverage AI technologies to optimize decision-making processes, drive significant business outcomes, and collaborate effectively with stakeholders from various backgrounds.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------TEACHING EXPERIENCE-----------------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingF
      {Head Teaching Assistant - Advanced Programming}{}
      {Supervisor: \href{https://ir.linkedin.com/in/seyed-abolghasem-mirroshandel-1a3a5950}{Dr. Ghasem Mirroshandel} - University of Guilan} 
      {Aug 2018 - Feb 2019}
  
    % taking too much space and it is not even comparable to what I did in other TAs
    % I have not even included Advanced programming and data structure helps 

    % \resumeSubheading
    %   {Teaching Assistant}{}
    %   {Algorithms Design} 
    %   {Feb 2017 - July 2017}{University of Guilan}
    %   \resumeItemListStart
    %     \resumeItem{Supervision: \href{https://www.linkedin.com/in/mojtaba-moe-shakeri-b34a2b6/}{Dr. Mojtaba Shakeri}}
    %     \resumeItem{Helped with grading of the assignments}
    %   \resumeItemListEnd
    
    \resumeSubheadingF
      {Head Teaching Assistant - Algorithms Design}{}
      {Supervisor: \href{https://www.linkedin.com/in/mojtaba-moe-shakeri-b34a2b6/}{Dr. Mojtaba Shakeri} - University of Guilan} 
      {Aug 2018 - Feb 2019}
    
    \resumeSubheadingF
      {Head Teaching Assistant - Computational Intelligence}{}
      {Supervisor: \href{https://www.linkedin.com/in/mojtaba-moe-shakeri-b34a2b6/}{Dr. Mojtaba Shakeri} - University of Guilan}
      {Feb 2018 - Jul 2018}

    \vspace{10pt}
    As a teaching assistant, I \textbf{taught} Java in the Advanced Programming course, \textbf{designed and graded assignments}, and \textbf{evaluated the final project}. For the Algorithm Design and Computational Intelligence courses, I held \textbf{weekly Q\&A sessions}, graded assignments, and \textbf{created pratical programming tasks} for Computational Intelligence.
    
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------VOLUNTARY ACTIVITIES (DEPRECATED - TOO LONG)-----------------
% \section{Voluntary Activities}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Mentor and Lecturer}{}
%       {An Open and Free Organization For Introducing AI and Mentorship} 
%       {2018 - 2021}{\href{http://schoolofai.ir/}{Rasht School of AI}}
%       \resumeItemListStart
%         \resumeItem{Held lectures around applications of AI, particularly digital image processing (\href{https://github.com/rasht-school-of-ai/Meetup-Materials}{Slides})}
%         \resumeItem{Mentored a few students who were interested in artificial intelligence and its applications}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd

%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Organizer and Mentor}{}
%       {An Open and Free Organization For Sharing Ideas, Showcasing Projects, and Mentoring Students} 
%       {2019 - 2021}{\href{http://iust-projects.ir/}{IUST Projects}}
%       \resumeItemListStart
%         \resumeItem{Attempted to challenge the university's siloed culture through open scientific/general discussions}
%         \resumeItem{Mentored junior students in preparation for going through the M.Sc thesis process, from ideation to publishing}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd

%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Member}{}
%       {Official forum with +50K members and authors of the PyTorch} 
%       {2018 - 2022}{{Official PyTorch Forum}}
%       \resumeItemListStart
%         \resumeItem{A top member (15th) with 183 solutions and 566 posts (\href{https://discuss.pytorch.org/u/Nikronic/}{summary})}
%         \resumeItem{Commended by \href{https://twitter.com/ThomasViehmann/status/1309794697049714689}{Thomas Viehmann} for insightful posts}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd
%-------------------------------------------

%-----------VOLUNTARY ACTIVITIES-----------------
\section{Voluntary Activities}
\resumeSubHeadingListStart
  \resumeSubheadingF
    {Mentor, Lecturer, and Organizer}{}
    {Rasht School of AI, IUST Projects, and PyTorch Forum}{2018 - 2022}
    \resumeItemListStart
      \resumeItem{\textbf{Lecturing:} Delivered talks on AI applications, focusing on digital image processing (\href{https://github.com/rasht-school-of-ai/Meetup-Materials}{Slides})}
      \resumeItem{\textbf{Mentorship:} Guided students in AI and M.Sc thesis processes, from ideation to publication}
      \resumeItem{\textbf{Organizing:} Facilitated open discussions at IUST to promote collaboration and challenge the siloed culture}
      \resumeItem{\textbf{Community Engagement:} Active in the PyTorch Forum, ranking 15th with 183 solutions and 566 posts (\href{https://discuss.pytorch.org/u/Nikronic/}{summary}); praised for insightful contributions by \href{https://twitter.com/ThomasViehmann/status/1309794697049714689}{Thomas Viehmann}}
    \resumeItemListEnd
\resumeSubHeadingListEnd
%-------------------------------------------

%--------Research Interests------------
\section{Research Interests}
  \resumeSubHeadingListStart
    \resumeItem{Deep Learning and Machine Learning}
    \vspace{-5pt}
    \resumeItem{Computer Graphics and Physics-based Simulation} 
    \vspace{-5pt}
    \resumeItem{AI for Engineering and Science}
  \resumeSubHeadingListEnd
%-------------------------------------------

%---------Awards-----------------------
\section{Awards and Certificates}
\awarditemListStart
  \awarditem{Awarded for \textbf{dedication and leadership} at Nahal Gasht}{2023}
  \awarditem{Completed \textbf{training in Workplace Ethics and Professionalism}, Organizational Behavior, etc.}{2023}
  \awarditem{Accepted in M.Sc program as a \textbf{National Exceptional Talent}, with \textbf{Tuition Waiver} at IUST}{2019}
  \awarditem{\textbf{Ranked 3rd} among B.Sc graduates in Computer Engineering, with \textbf{Tuition Waiver} at the UoG}{2019}
  \awarditem{Participated in the Deep Learning Summer School at Gda\'{n}sk University of Technology}{2020}

\awarditemListEnd
%-------------------------------------------

%-----------REFEREES-----------------
\section{Referees}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. Vahid Babaei (Research Scientist)}{Saarbr{\"u}cken, Germany}
       {Role: Research project supervisor}
      {\href{mailto:vbabaei@mpi-inf.mpg.de}{vbabaei@mpi-inf.mpg.de}}{Max Planck Institute for Informatics}

    \resumeSubheading
      {Prof. Julian Panetta (Assistant Professor)}{Davis, USA}
       {Role: Research project supervisor}
      {\href{mailto:jpanetta@ucdavis.edu}{jpanetta@ucdavis.edu}}{University of California, Davis}
    
    \resumeSubheading
      {Dr. Mojtaba Shakeri (Research Scientist)}{Los Angeles, USA}
       {Role: Undergraduate mentor and instructor}
      {\href{mailto:mojtaba.shakeri@gmail.com}{mojtaba.shakeri@gmail.com}}{MercuryGate (prev. Assistant Professor at University of Guilan, Rasht, Iran)}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
