%-------------------------
% Resume in Latex
% Author : Nikan Doosti
%------------------------

\documentclass[letterpaper,11pt]{article}

% \include{command.tex}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\LinedItem}[1]{\item \begin{tabular}[t]{|p{10cm}}#1\end{tabular}}

\newcommand{\resumeSubheading}[5]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ 
      \textit{\small#3} & \textit{\small #4} \\
      \textit{#5} & 
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingF}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ 
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingN}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\ 
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\awarditem}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\ 
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\awarditemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\awarditemListEnd}{\end{itemize}\vspace{-5pt}}
    


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nikan Doosti}} (Officially: Mohammad DoostiLakhani) &
  Email: \href{mailto:nikan.doosti@outlook.com}{nikan.doosti@outlook.com}\\
   & Web: \href{https://www.nikronic.com/}{https://www.nikronic.com}
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience (Chronological)}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Full-time Machine Learning Engineer}{Karaj, Iran}
      {Applications of Data Science and Machine Learning in Tourism
      }
    {April 2022 - Present}{\href{https://nahalgasht.com/}{Nahal Gasht/Pana4}}
    
    \resumeItemListStart
      \resumeItem{Developed and implemented a new data architecture that reduced bad data by 35\%, resulting in increased accuracy of machine learning models.}
      \resumeItem{Designed and implemented a full pipeline of data extraction, transformation, and preprocessing dealing with low/unlabeled data regime.}
      \resumeItem{Created engaging and informative user interactions by integrating gamification objectives in designing and training machine learning models.}
      \resumeItem{Collaborated with employees, software engineers, and managers to revamp the data architecture and ensure smooth integration with existing systems.}
      \resumeItem{Utilized Python, PyTorch, SKlearn, Pandas, Snorkel, Docker, MLflow, Git, FastAPI, Godot, etc}
    \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{Saarbr{\"u}cken, Germany}
      {\href{http://aidam.mpi-inf.mpg.de/?view=home}{Artificial Intelligence aided Design and Manufacturing Group} 
      }{Jul 2020 - Mar 2021}{Max Planck Institute for Informatics}
     
      \resumeItemListStart
        \resumeItem{Novel self-supevised neural method for obtaining the optimum design showcased in Topology Optimization}
        \resumeItem{Supervision of \href{http://aidam.mpi-inf.mpg.de/?view=people_vahid} {\textbf{Dr. Vahid Babaei}}}
        \resumeItem{Collaboration of \href{https://www.julianpanetta.com/}{\textbf{Prof. Julian Panetta}} at University of California, Davis, USA.}
        \resumeItem{Physics-based simulation of stiffness of the obtained design}
        \resumeItem{Generative continuous design via a single fixed mesh through controlling the frequencies}
        \resumeItem{This project has been published and presented in ACM Symposium on Computational Fabrication 2021}
        \resumeItem{This project was defined as my master's thesis}
        \resumeItem{I spent 1500+ hours until the submission of concluding paper}
      \resumeItemListEnd
    
    \resumeSubheadingF
      {Award}{}
      {Accepted in MSc program without Entrance Exam as an Exceptional Talent}{Sep 2019}

    \resumeSubheadingF
      {Award}{}
      {Tuition Waiver, MSc, Iran University of Science and Technology}{Sep 2019}
    
    \resumeSubheading
      {Organizer and Mentor}{}
      {Voluntary activity} 
      {Dec 2019 - Jul 2021}{\href{http://iust-projects.ir/}{IUST Projects}}
      \resumeItemListStart
        \resumeItem{Attempted to challenge the university's siloed culture through open scientific/general discussions}
        \resumeItem{Mentored junior students in preparation for going through the M.Sc thesis process, from ideation to publishing}
      \resumeItemListEnd

    \resumeSubheadingF
      {Master of Computer Engineering - Artificial Intelligence}{Tehran, Iran}
      {Iran University of Science and Technology (IUST)}{Sep 2019 - Dec 2022}
      \resumeItemListStart
        \resumeItem{\href{http://www.iust.ac.ir/}{IUST} is one of the most prestigious universities of the country}
        \resumeItem{\textbf{Thesis:} High Resolution Neural Topology Optimization via Differentiable Physics Engine}
        \resumeItem{\textbf{Defense:} Defended with Full mark on 22 Oct 2022}
        \resumeItem{\textbf{GPA:} 17.17/20.00}
      \resumeItemListEnd

    \resumeSubheadingF
      {Long Vacation}{Iran}
      {Travel}{Aug 2019 - Sep 2019}

    \resumeSubheadingF
      {Award}{}
      {Ranked 3rd among BSc graduates in Computer Engineering, University of Guilan}{Jul 2019}
    

    \resumeSubheading
      {Mentor and Lecturer}{}
      {Voluntary activity} 
      {Dec 2018 - Present}{\href{http://schoolofai.ir/}{Rasht School of AI}}
      \resumeItemListStart
        \resumeItem{Held lectures around applications of AI, particularly digital image processing (\href{https://github.com/rasht-school-of-ai/Meetup-Materials}{Slides})}
        \resumeItem{Mentored a few students who were interested in artificial intelligence and its applications}
      \resumeItemListEnd

    \resumeSubheading
      {Head Teaching Assistant}{}
      {Advanced Programming} 
      {Aug 2018 - Feb 2019}{University of Guilan}
      \resumeItemListStart
        \resumeItem{Supervision: \href{https://ir.linkedin.com/in/seyed-abolghasem-mirroshandel-1a3a5950}{Dr. Ghasem Mirroshandel}}
        \resumeItem{Taught undergraduate students Java programming language in weekly 4-hour sessions}
        \resumeItem{Designed and graded their assignments and the final project}
      \resumeItemListEnd
     
    \resumeSubheading
      {Head Teaching Assistant}{}
      {Algorithms Design} 
      {Aug 2018 - Feb 2019}{University of Guilan}
      \resumeItemListStart
        \resumeItem{Supervision: \href{https://www.linkedin.com/in/mojtaba-moe-shakeri-b34a2b6/}{Dr. Mojtaba Shakeri}}
        \resumeItem{Held weekly 2-hour QA sessions and graded the assignments}
      \resumeItemListEnd
 
    \resumeSubheading
      {Head Teaching Assistant}{}
      {Computational Intelligence} 
      {Feb 2018 - Jul 2018}{University of Guilan}
      \resumeItemListStart
        \resumeItem{Supervision: \href{https://www.linkedin.com/in/mojtaba-moe-shakeri-b34a2b6/}{Dr. Mojtaba Shakeri}}
        \resumeItem{Designed programming assignments}
        \resumeItem{Held weekly 2-hour QA sessions and graded all the assignments}
      \resumeItemListEnd

    \resumeSubheadingF
      {Internship}{Tehran, Iran}
      {\href{https://matris.co.ir/n/}{Matris Co}}{Jul 2018 - Sep 2018}
      \resumeItemListStart
         \resumeItem{Examination, troubleshooting, and repair of computers}
         \resumeItem{Research and investigation in technical areas to optimize the repair process}
       \resumeItemListEnd

    \resumeSubheadingN{No Activity}{Jul 2017 - Sep 2017}

    \resumeSubheadingN{No Activity}{Jul 2016 - Sep 2016}
    
    \resumeSubheadingF
      {Award}{}
      {Tuition Waiver, BSc, University of Guilan}{Aug 2015}
    
    \resumeSubheadingF
      {Bachelor of Computer Engineering}{Rasht, Iran}
      {\href{https://guilan.ac.ir/}{University of Guilan}}{Aug 2015 - Aug 2019}
      \resumeItemListStart
         \resumeItem{\textbf{Final Project:} Rescreening of Halftone Images via Data-Driven Deep Learning Methods}
         \resumeItem{\textbf{Class Rank:} 3}
         \resumeItem{\textbf{GPA:} 18.64/20.00}
       \resumeItemListEnd
      
    \resumeSubheadingF
      {Pre-university diploma of Mathematics and Physics}{Karaj, Iran}
      {Shahid Mire-ei Highschool}{Sep 2014 - Aug 2015}
      
    \resumeSubheadingN{No Activity}{Jun 2014 - Sep 2014}
    
    \resumeSubheadingF
      {High school diploma of Mathematics and Physics}{Kamal Shahr, Iran}
      {Malek Ashtar Highschool}{Sep 2011 - Jun 2014}
    
  \resumeSubHeadingListEnd
%-------------------------------------------


%--------Publications------------------
\section{Publications}
 \resumeSubHeadingListStart
   \resumeItem{\textbf{Doosti, Nikan}, Julian Panetta, and Vahid Babaei. "Topology Optimization via Frequency Tuning of Neural Design Representations." In Symposium on Computational Fabrication, pp. 1-9. 2021. (\href{https://dl.acm.org/doi/abs/10.1145/3485114.3485124}{ACM})}
\resumeSubHeadingListEnd
%-------------------------------------------

%--------TALKS------------------
\section{Talks}
 \resumeSubHeadingListStart
   \resumeItem{Doosti, Nikan. 2022. "Neural Design Representations." Toronto Geometry Colloquium. March 4, 2022. toronto-geometry-colloquium.github.io. (Length: 10 mins., \href{https://youtu.be/FdPwG2kNv0M}{Video})} 
\resumeSubHeadingListEnd
%-------------------------------------------

%--------Research Interests------------
\section{Research Interests}
  \resumeSubHeadingListStart
    \resumeItem{Deep Learning}
    \vspace{-5pt}
    \resumeItem{Physics-based Simulation}
    \vspace{-5pt}
    \resumeItem{Computer Graphics} 
    \vspace{-5pt}
    \resumeItem{Computational Fabrication}
    \vspace{-5pt}
    \resumeItem{Digital Image Processing}
    \vspace{-5pt}
    \resumeItem{Computational Neuroscience}
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------REFEREES-----------------
\section{Referees}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. Vahid Babaei (Research Scientist)}{Saarbr{\"u}cken, Germany}
       {Role: Research project supervisor}
      {\href{mailto:vbabaei@mpi-inf.mpg.de}{vbabaei@mpi-inf.mpg.de}}{Max Planck Institute for Informatics}

    \resumeSubheading
      {Prof. Julian Panetta (Assistant Professor)}{Davis, USA}
       {Role: Research project supervisor}
      {\href{mailto:jpanetta@ucdavis.edu}{jpanetta@ucdavis.edu}}{University of California, Davis}
    
    \resumeSubheading
      {Dr. Mojtaba Shakeri (Research Scientist)}{Los Angeles, USA}
       {Role: Undergraduate mentor and instructor}
      {\href{mailto:mojtaba.shakeri@gmail.com}{mojtaba.shakeri@gmail.com}}{MercuryGate (prev. Assistant Professor at University of Guilan, Rasht, Iran)}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
